\boldmath Disconnected pseudo-$C_\ell$ covariances for projected large-scale structure data

### 2019-06-24 draft/paper.tex
added comma + Fig -> Figure

      We explore $\log p(\vec{\theta}|\hat{\bf C})$ for of two parameters $\vec{\theta}\equiv(\Omega_M,\sigma_8)$, for a data vector composed of all possible auto- and cross-correlations between $\delta$ and $\gamma_E$ in the case of two redshift bins. In this simple two-dimensional scenario we simply sample the distribution in a regular grid of 100 by 100 points for each parameter. We construct a data vector $\hat{\bf C}$ from the theoretical prediction for the experimental setup described in Section \ref{ssec:results.sims}, and produce theoretical predictions for it at each grid point using {\tt CCL}. Note that, when evaluating the posterior for the sample covariance matrix, one needs to correct for the finite number of simulations used to construct the covariance. In most situations this can be done simply by rescaling the inverse covariance matrix by a factor  given by \cite{2007A&A...464..399H}
      \begin{equation}\label{eq:hartlap}
        {\rm Cov}^{-1}\,\longrightarrow \frac{N_s-2-N_{\rm data}}{N_s-1}\,{\rm Cov}^{-1},
      \end{equation}
      where $N_s=20,000$ is the number of samples used to estimate the covariance, and $N_{\rm data}=3510$ is the number of data points.

      The 68\% and 95\% confidence level contours associated with the posterior distributions for the sample covariance and the NKA estimator are shown in Fig. \ref{fig:contours}. We find that both distributions agree with each other remarkably well, and that the $1\sigma$ errors for each parameter agree for both covariances up to $0.3\%$. Note that, since we have not included any statistical noise in the data vector $\hat{\bf C}$, the relative bias between both distributions is zero by construction (since Eq. \ref{eq:parpos} is bounded from below by zero). When adding Gaussian statistical noise compatible with the sample covariance matrix, we observe small differences (smaller than 0.3$\sigma$) in the best fit parameters found with both covariance matrices. These differences, however, are not systematic, and we have verified that averaging over several noise realizations does not yield biased best-fit parameters.

>>>>

      We explore $\log p(\vec{\theta}|\hat{\bf C})$ for of two parameters
      $\vec{\theta}\equiv(\Omega_M,\sigma_8)$, for a data vector composed of
      all possible auto- and cross-correlations between $\delta$ and
      $\gamma_E$ in the case of two redshift bins. In this simple
      two-dimensional scenario, we simply sample the distribution in a regular grid of 100 by 100 points for each parameter. We construct a data vector $\hat{\bf C}$ from the theoretical prediction for the experimental setup described in Section \ref{ssec:results.sims}, and produce theoretical predictions for it at each grid point using {\tt CCL}. Note that, when evaluating the posterior for the sample covariance matrix, one needs to correct for the finite number of simulations used to construct the covariance. In most situations this can be done simply by rescaling the inverse covariance matrix by a factor  given by \cite{2007A&A...464..399H}
      \begin{equation}\label{eq:hartlap}
        {\rm Cov}^{-1}\,\longrightarrow \frac{N_s-2-N_{\rm data}}{N_s-1}\,{\rm Cov}^{-1},
      \end{equation}
      where $N_s=20,000$ is the number of samples used to estimate the covariance, and $N_{\rm data}=3510$ is the number of data points.

      The 68\% and 95\% confidence level contours associated with the
      posterior distributions for the sample covariance and the NKA estimator
      are shown in Figure~\ref{fig:contours}. We find that both distributions agree with each other remarkably well, and that the $1\sigma$ errors for each parameter agree for both covariances up to $0.3\%$. Note that, since we have not included any statistical noise in the data vector $\hat{\bf C}$, the relative bias between both distributions is zero by construction (since Eq. \ref{eq:parpos} is bounded from below by zero). When adding Gaussian statistical noise compatible with the sample covariance matrix, we observe small differences (smaller than 0.3$\sigma$) in the best fit parameters found with both covariance matrices. These differences, however, are not systematic, and we have verified that averaging over several noise realizations does not yield biased best-fit parameters.
